Ignition of Fuel Beds by Firebrands

### 2022-04-04 litreview.tex
Working on updates to the background chapter

\chapter{Literature Review}
\label{part:literature}

>>>>

\chapter{Background}
\label{part:literature}
    This chapter provides a discussion of the background and motivation of this work in further depth than the manuscripts in this dissertation.  Here, a general overview of ignitions as a threat to structures and fire spread as well as the current state of knowledge and predictive capabilities is communicated. Each manuscript includes a relevant and more detailed literature review pertaining to the specific objective of the work.

    \section{Historical Perspective}
    Wild fires have been an integral part of many ecosystems for millennia and are often beneficial or required for maintaining a healthy ecosystem. As beneficial as they may be to the natural enviornment wildfires pose significant risk to the built environment. As communities around the world have expanded communities outward into environments that support wildfires (e.g., forests and grasslands) the risk of destruction of structures by wildfires has increased. In the United States 91\% of the Wildland Urban Interface \nomenclature{WUI}{Wildland Urban Interface} growth of 189,000\si{\kilo\meter\squared} (larger than the state of Washington) development between 1990 and 2010 is occupied by homes~\cite{Radeloff2017} and has continued to grow on recent years. 
    \section{The ignition process}

    \section{Current Challenges}

    \section{State of Knowledge/guiding factors}
